Simulation Study of Angular Resolution of a New Electromagnetic Sampling Calorimeter

### 2022-05-31 paper.tex
updates

We studied a correlation between byperparameters of the XGB model and the angular resolution. The test scans the evaluated angular resolution with different hyperparameters. Figure~\ref{fig:par_scan} shows the test results with N\_estimators and Max. depth. N\_estimators defines the maximum allowed number of decision trees to be developed, and the Max. depth defines the complexity of the structure of decision trees. The best hyperparameter combination was searched for in terms of the angular resolution. As a results, N\_estimators and Max. depth are set to 300 and 100, respectively. Similar tests were also performed for different hyperparameters. The best values for other hyperparameters are displayed in Tab.~\ref{tab:XgbPar}. Other hyperparameters tuned in this study are Subsample, Learning rate, and Gamma. Subsample controls the fraction of total event samples for each boosting procedure, and Learning rate weights a decision tree to be added onto the current model. Lastly, Gamma regulates the evaluation of each decision tree.

\begin{table}[hbt!]{\small
\centering
\caption{Hyperparameters of the XGB model}
\begin{tabular}{cccc}
\hline 
Parameter & Function & Default value & Used value \\ \hline 
N\_estimators & The number of decision trees & N.A. & 300 \\  
Max. depth & Possible maximum depth of tree structure & 6 & 100 \\ 
Subsample & Fraction of total data used for a single decision & 1 & 0.8 \\ 
Learning rate & Step length for calculation & 0.3 & 0.02 \\ 
Gamma & Requirement on minimum loss function & 0 & 0 \\ 
\hline
\end{tabular}
\label{tab:XgbPar}
}\end{table}

@@

Angular resolutions were deduced with varying strip widths from 5 mm to 35 mm as shown in Fig.~\ref{fig:angle_reco_width}. The 15-mm-wide strips yield the best angular resolution of 1.23~$\pm$~0.01$^{\circ}$. The shorter the strip width is, the larger size of features, which can influence negatively in machine learning. For longer strips, the EM shower information can hardly be obtained.

@@

Furthermore, incidence angles are reconstructed with the front layers of $4.6X_{0}$ in which 99\% of incident photons generate EM showers. Figure~\ref{fig:angle_reco_layer} (a) shows reconstructed angles using front 24 layers of the detector, which correspond to 4.6$X_{0}$ for 1-GeV photons. A fraction of photons failed to be reconstructed due to the lack of active layers. The failed events are represented as a delta function near 0, and such events are removed by requiring the total energy deposit to be larger than 10~MeV, 1\% of the incident energy. The angular resolution with the front layer is estimated to be 1.33~$\pm$~0.01$^{\circ}$ while possessing inefficiency estimated to be 5.8\%.

>>>>

We studied a correlation between byperparameters of the XGB model and the angular resolution. The test scans the evaluated angular resolution with different hyperparameters. Figure~\ref{fig:par_scan} shows the test results with N\_estimators and Max. depth. N\_estimators defines the maximum allowed number of decision trees to be developed, and the Max. depth defines the complexity of the structure of decision trees. The best hyperparameter combination was searched for in terms of the angular resolution. As a results, N\_estimators and Max. depth are set to 300 and 100, respectively. Similar tests were also performed for different hyperparameters. The best values for other hyperparameters are displayed in Tab.~\ref{tab:XgbPar}. Other hyperparameters tuned in this study are Subsample, Learning rate, and Gamma. Subsample controls the fraction of total event samples for each boosting procedure, and Learning rate weights a decision tree to be added onto the current model. Lastly, Gamma regulates the evaluation of each decision tree. It is also worth mentioning that the fraction of the tail is not changing from 2\%.
\begin{table}[hbt!]{\small
\centering
\caption{Hyperparameters of the XGB model}
\begin{tabular}{cccc}
\hline 
Parameter & Function & Default value & Used value \\ \hline 
N\_estimators & The number of decision trees & N.A. & 300 \\  
Max. depth & Possible maximum depth of tree structure & 6 & 100 \\ 
Subsample & Fraction of total data used for a single decision & 1 & 0.8 \\ 
Learning rate & Step length for calculation & 0.3 & 0.02 \\ 
Gamma & Requirement on minimum loss function & 0 & 0 \\ 
\hline
\end{tabular}
\label{tab:XgbPar}
}\end{table}

@@

Angular resolutions were deduced with varying strip widths from 5 mm to 35 mm as shown in Fig.~\ref{fig:angle_reco_width}. The 15-mm-wide strips yield good angular resolution of 1.23~$\pm$~0.01$^{\circ}$. The shorter the strip width is, the larger size of features, which can influence negatively in machine learning. For longer strips, the EM shower information can hardly be obtained.

@@

Furthermore, incidence angles are reconstructed with the front layers of $ 6.2X_{0}$ in which 99\% of incident photons generate EM showers. Figure~\ref{fig:angle_reco_layer} (a) shows reconstructed angles using front 24 layers of the detector, which correspond to 4.6$X_{0}$ for 1-GeV photons. A fraction of photons failed to be reconstructed due to the lack of active layers. The failed events are represented as a delta function near 0, and such events are removed by requiring the total energy deposit to be larger than 10~MeV, 1\% of the incident energy. The angular resolution with the front layer is estimated to be 1.33~$\pm$~0.01$^{\circ}$ while possessing inefficiency estimated to be 5.8\%.
